A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Deduplicate

With these definitions established, we now present \McSplit, a branch and bound
algorithm which uses a new vertex-labelling scheme to avoid explicitly
maintaining the set of feasible mappings for each vertex in $\V(\graphG)$.

\McSplit\ finds a maximum-cardinality mapping $M^* = \{(v_1, w_1), \dots,
(v_{m}, w_{m})\}$ with $|M^*| = m$ vertex pairs, where the $v_i$ are distinct members of $\V(\graphG)$ and the
$w_i$ are distinct vertices of $\V(\graphH)$, such that $v_i$ and $v_j$ are adjacent
in $\graphG$ if and only if $w_i$ and $w_j$ are adjacent in $\graphH$. 
Given such a mapping, the subgraph of $\graphG$ induced by $\{v_i, \dots, v_{m}\}$
and the subgraph of $\graphH$ induced by $\{w_i, \dots, w_{m}\}$ are a maximum
common subgraph.

>>>>

With these definitions established, we now present \McSplit. This algorithm
finds a maximum-cardinality mapping $M^* = \{(v_1, w_1), \dots, (v_{m},
w_{m})\}$ with $|M^*| = m$ vertex pairs, where the $v_i$ are distinct members
of $\V(\graphG)$ and the $w_i$ are distinct vertices of $\V(\graphH)$, such
that $v_i$ and $v_j$ are adjacent in $\graphG$ if and only if $w_i$ and $w_j$
are adjacent in $\graphH$.  Given such a mapping, the subgraph of $\graphG$
induced by $\{v_i, \dots, v_{m}\}$ and the subgraph of $\graphH$ induced by
$\{w_i, \dots, w_{m}\}$ are a maximum common subgraph.
